Articles

### 2017-04-23 articles/articles.Rmd
fix typo in multiple testing

@@

- Why Companies like Lyft, Uber, Postmates, Instacart etc Will Never Be Profitable. [Linkedin](https://www.linkedin.com/pulse/why-companies-like-lyft-uber-postmates-instacart-etc-never-fabode)
- The New 'Must Haves' for Mobile Apps to Succeed Today. [[First Round Review](http://firstround.com/review/the-new-must-haves-for-mobile-apps-to-succeed-today/)]
- 'Amazon is not your friend'. [[Linkedin](https://www.linkedin.com/pulse/amazon-your-friend-caroline-fairchild)]
    - The only way to survive is to build a brand that can grow without Amazon’s distribution.
    - Amazon hasn’t proven that it can build inspirational brands. While they have mastered the ability to get customers commodity products, no one goes to Amazon to discover something they didn’t already know about.
- Facebook is the new Excel. [[blog](http://alexmuir.com/facebook-is-the-new-excel)]
- We need companies to start innovating instead of imitating success stories. [[Hustle](http://thehustle.co/snapchat-vs-spacex-battle-of-the-imitators-and-innovators)]
- My 4+ Years At Uber Taught Me These Key Lessons. 1. May the supply be with you ; 2. Don't listen, show them. [[Linkedin](https://www.linkedin.com/pulse/three-things-i-learned-during-4-years-uber-michael-pao)]

>>>>

- 2017.04.02 | The Startup Founder’s Guide to Analytics. [Medium](https://thinkgrowth.org/the-startup-founders-guide-to-analytics-1d2176f20ac1)

@@

- How Data Science Is Transforming Health Care. [O'Reilly](https://www.oreilly.com/ideas/how-data-science-is-transforming-health-care)
    - Just like targeted ads, we should have targeted health care
- Why Companies like Lyft, Uber, Postmates, Instacart etc Will Never Be Profitable. [Linkedin](https://www.linkedin.com/pulse/why-companies-like-lyft-uber-postmates-instacart-etc-never-fabode)
- The New 'Must Haves' for Mobile Apps to Succeed Today. [[First Round Review](http://firstround.com/review/the-new-must-haves-for-mobile-apps-to-succeed-today/)]
- 'Amazon is not your friend'. [[Linkedin](https://www.linkedin.com/pulse/amazon-your-friend-caroline-fairchild)]
    - The only way to survive is to build a brand that can grow without Amazon’s distribution.
    - Amazon hasn’t proven that it can build inspirational brands. While they have mastered the ability to get customers commodity products, no one goes to Amazon to discover something they didn’t already know about.
- Facebook is the new Excel. [[blog](http://alexmuir.com/facebook-is-the-new-excel)]
- We need companies to start innovating instead of imitating success stories. [[Hustle](http://thehustle.co/snapchat-vs-spacex-battle-of-the-imitators-and-innovators)]
- My 4+ Years At Uber Taught Me These Key Lessons. 1. May the supply be with you ; 2. Don't listen, show them. [[Linkedin](https://www.linkedin.com/pulse/three-things-i-learned-during-4-years-uber-michael-pao)]
